Note on Boundary condition and choice of grid

### 2024-06-28 write2/manuscript_part2_2024.tex
started work on Sec. 4

% z0
A key parameter governing the turbulent state of the flow is the geostrophic drag: it puts the surface friction in relation to the geostrophic wind and thus illustrates the conversion of mean-flow kinetic energy to turbulence. The ratio of $u_{\star}$ resulting from the simulations to the theoretical value $u_{\star,th}$ are shown in Tbl. \ref{simulation_results}. All values are close to one, while the strongest deviations are observed for the simulations with the coarsest resolutions. A slight dependence on the resolution can be observed for Re1, as $u_\star$ steadily approaches $u_{\star,th}$ with increasing resolution. For Re2 and Re3, all but the coarsest resolution nearly exactly match the theoretical value. The choice of $z_0$ and the geostrophic wind $G$ determine the magnitude of $u_\star$ in a non-trivial way. From a top perspective, the horizontal velocity increases from its geostrophic value to the supergeostrophic maximum and then decreases with decreasing height. The horizontal mean velocity at the grid point closest to $z^-=0.1$ is used to calculate $u_\star$ according to eq. \ref{us_mean}. It is remarkable that the choice of $z_0^+=0.1031$ leads to a value of $u_{\star}$ very close to the prediction by semi-empirical considerations (cf. \cite{spalart1989theoretical}).

@@

%alpha
Another key parameter of the Ekman flow is the surface veering angle $\alpha_\star$ between the directions of the negative surface shear stress and the geostrophic wind. For the LES, the direction of the negative stress is represented by the first derivatives of the velocity components calculated by 3rd order forward finite differences: $\alpha_\star = \tan^{-1}(\langle \partial v/\partial z\rangle_0/\langle \partial u/\partial z\rangle_0)-\tan^{-1}(V_G/U_G)$. Table \ref{simulation_results} shows that nearly all LES yield an $\alpha_\star$ smaller than the theoretical value $\alpha_{\star,th}$. In general, we observe an increase of $\alpha_\star$ with resolution. The finest resolution of $Re2$ and $Re3$ generally align closely with the theoretical direction while for $Re1\_200$ still 0.9° is missing. Fig. \ref{3Re_hodograph} illustrates that this is not caused by poor quality of the simulation since all of the simulations of $Re1$ follow the theoretical hodograph quite closely and even overestimate the angle at the respective height by a little. In contrast to the higher $\RE$, the veering of the wind vector continues in the lower parts of the boundary layer. Hence, for the low-$\RE$ case, the general observation of a higher $\alpha_\star$ with finer resolution is also caused by the approach of the final $\alpha_\star$ with decreasing height of the first grid point. In general, the finer resolved simulations show veering angles that are very close to the theoretic predictions.

>>>>

% z0
The geostrophic drag $Z=u_\star/G$ quantifies the conversion of mean-flow kinetic energy ($G^2$) to turbulence ($u_{\star}^2$). The ratio of $u_{\star}$ resulting from the simulations to the theoretical value $u_{\star,th}$ are shown in Tab. \ref{simulation_results}. All values are close to one, while the strongest deviations are observed for the simulations with the coarsest resolutions. A slight dependence on the resolution can be observed for Re1, as $u_\star$ steadily approaches $u_{\star,th}$ with increasing resolution. For Re2 and Re3, all but the coarsest resolution nearly exactly match the theoretical value. The choice of $z_0$ and the geostrophic wind $G$ determine the magnitude of $u_\star$ in a non-trivial way. From a top perspective, the horizontal velocity increases from its geostrophic value to the supergeostrophic maximum and then decreases with decreasing height. The horizontal mean velocity at the grid point closest to $z^-=0.1$ is used to calculate $u_\star$ according to Eq.~(\ref{us_mean}). It is remarkable that the choice of $z_0^+=0.1031$ leads to a value of $u_{\star}$ very close to the prediction by semi-empirical considerations (cf. \cite{spalart1989theoretical}).

@@

%alpha
The surface veering $\alpha_\star$ is key to quantify the Ekman pumping and of central relevance for larger-scale applications. For the LES, we use the first derivatives of the velocity components calculated by 3$^\text{rd}$-order forward finite differences to estimate $\alpha_\star$:
\begin{align}
  \alpha_\star = \arctan\left(\left.\left\langle \frac{\partial v}{\partial z}\right\rangle_0\right/\left\langle \frac{\partial u}{\partial z}\right\rangle_0\right)-\arctan\left(\frac{V_G}{U_G}\right).
\end{align}
 Table \ref{simulation_results} shows that nearly all LES yield an $\alpha_\star$ smaller than the theoretical value $\alpha_{\star,\text{th}}$. In general, we observe an increase of $\alpha_\star$ with resolution. The finest resolution of Re2 and Re3 generally align closely with the theoretical direction while for Re1\_200 still 0.9° is missing. Fig. \ref{3Re_hodograph} illustrates that this is not caused by poor quality of the simulation since all of the simulations of Re1 follow the theoretical hodograph quite closely and even overestimate the angle at the respective height by a little. In contrast to the higher $\RE$, the veering of the wind vector continues in the lower parts of the boundary layer. Hence, for the low-$\RE$ case, the general observation of a higher $\alpha_\star$ with finer resolution is also caused by the approach of the final $\alpha_\star$ with decreasing height of the first grid point. In general, the finer resolved simulations show veering angles that are very close to the theoretical prediction.
